Computing volume via non-linear rectangular prisms

### 2019-08-07 Cav2D/article-template.tex
added more text to two dimensional definition

\noindent
Alternatively, the area of $R$ can also be determined via the Cavalieri integral:
\begin{equation}
\label{eq:caval1}
\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
\end{equation}
with $\Delta x_i^1 = x_{i+1}^1 - x_i^1$. Furthermore, the partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Let us review why this is in fact the case:
\begin{itemize}
 \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
 \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
 \item $f(x_i^2)\Delta x_i^1$ represents the height of a non-rectangular integration strip (due to Cavalieri's principle).
 \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
 \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
\end{itemize}

@@

Note that $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ is the line of intersection between the planes $2x$ and $y$. Furthermore, the line 
$\mathbf{c}(t)$ passes through the origin. The line $\mathbf{c}(t)$ is depicted and labelled in Figure~\ref{fig:prismatoid_solid}. Let 
\begin{equation}
R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber
\end{equation}
and
\begin{equation}
S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\geq x\geq -\sfrac{1}{3}y+\sfrac{16}{3}, \sfrac{1}{2} x + 4\geq y \geq \sfrac{1}{2} x + 6 \}. \nonumber
\end{equation}
The region $S$ and $R$ is depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}. Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^2,0 \right >$ intersects the 
$xy$-plane to the $xy$--coordinate $(x_i^2,y_i^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^2,0 \right >$ intersects $f(x,y)$.

>>>>

\noindent
Alternatively, the area of $R$ can also be determined via the Cavalieri integral:
\begin{equation}
\label{eq:caval1}
\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
\end{equation}
with $\Delta x_i^1 = x_{i+1}^1 - x_i^1$. Furthermore, the partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Let us review why this is in fact the case:
\begin{itemize}
 \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
 \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
 \item $f(x_i^2)\Delta x_i^1$ represents the area of a non-rectangular integration strip (due to Cavalieri's principle).
 \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
 \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
\end{itemize}

@@

Note that $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ is the line of intersection between the planes $2x$ and $y$. Furthermore, the line 
$\mathbf{c}(t)$ passes through the origin. The line $\mathbf{c}(t)$ is depicted and labelled in Figure~\ref{fig:prismatoid_solid}. Let 
\begin{equation}
R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber
\end{equation}
and
\begin{equation}
S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\geq x\geq -\sfrac{1}{3}y+\sfrac{16}{3}, \sfrac{1}{2} x + 4\geq y \geq \sfrac{1}{2} x + 6 \}. \nonumber
\end{equation}
The region $S$ and $R$ is depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}. Let us now subdivide $R$ into 
subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j$. 
Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 
$xy$-plane to the $xy$--coordinate $(x_i^2,y_j^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$. 
We can now approximate $\mathcal{S}_V$ via:
\begin{equation}
V_{\mathcal{S}} \approx \sum_{i=0}^n \sum_{j=0}^m f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1.
\end{equation}
